\documentclass[12pt,letterpaper]{article}

\PassOptionsToPackage{hyphens}{url}
\usepackage[
  pdftex, 
  bookmarksopen=true, 
  bookmarksnumbered=true,
  pdfstartview=FitH, 
  breaklinks=true, 
  urlbordercolor={0 1 0}, 
  citebordercolor={0 0 1}]
  {hyperref}

\usepackage{setspace}
\onehalfspacing

% === MARGINS ===
\addtolength{\hoffset}{-0.75in} 
\addtolength{\voffset}{-1.25in}
\addtolength{\textwidth}{1.5in} 
\addtolength{\textheight}{2.25in}

% == ENVS ==
\newenvironment{tightcenter}{%
  \setlength\topsep{0pt}
  \setlength\parskip{0pt}
  \begin{center}
}{
  \end{center}
}

% == PACKS ==
\usepackage{color,soul}
\usepackage{graphicx} % to use pngs in tex (include graphix)
\usepackage{calc} % To scale \pagewidth with \real{float}
\usepackage{pgfplots} % To draw histogram
\pgfplotsset{compat=1.17} % request specific version of pgfplots
\usepackage{calc} % to use \real for text -> numeric
\usepackage{pgf} % to store numeric variables
\usepackage{subcaption} % to place two figures horizontally
\usepackage{caption} % to refer subfigure
\renewcommand{\thesubfigure}{(\alph{subfigure})}
\captionsetup[sub]{labelformat=simple}

\usepackage{tikz}
\usetikzlibrary{automata,positioning}
\usetikzlibrary{arrows.meta, positioning, automata}
\usetikzlibrary{spy}

\tikzset{
  font={\fontsize{10pt}{0}\selectfont}}
\usepackage{forest}
\tikzset{
  Decision/.style = {%
    draw,
    line width=1.4pt
  },
  Lottery/.style = {%
    draw,
    line width=1.4pt
  },
  Outcome/.style = {%
    circle,
    minimum width=3pt,
    fill,
    inner sep=0pt
  }
}
\usepackage{csquotes}
\usepackage{lipsum}
\usetikzlibrary{arrows.meta,automata,positioning} % to draw directed-weighted-graph


\usepackage{amsmath, amssymb, latexsym} % NN
\usepackage{tikz}% NN
\usetikzlibrary{decorations.pathreplacing}% NN
\usetikzlibrary{fadings}% NN


\usepackage{xltabular}
\usepackage{booktabs}

\usepackage[breakable]{tcolorbox} % to add factual asepct inside a frame

\usepackage[title]{appendix}

% == Checkmarks == 
\usepackage{bbding}
\usepackage{pifont}
\usepackage{wasysym}
\usepackage{amssymb}
% ================

% == BIBS ==
\usepackage{natbib}

\usepackage{diagbox}

\bibliographystyle{apsr}


% == SPACES == 

% == CMMDS ==
\newcommand{\tit}{
\bf 
Mapping Regulatory Network of WTO Dispute Settlement Body Using Deep Learning
}
\newcommand\spacingset[1]{\renewcommand{\baselinestretch}
{#1}\small\normalsize}

% == VARS == 
\pgfmathsetmacro{\heatmap}{1}

% == START (PageCounter, Mode)
\begin{document}

\spacingset{1.25}

\setcounter{page}{0}
\vspace{-.1in}

% == TITLE (includes DraftDate)
{\title{
    \tit
  }
  \author{Suyeol Yun
  }
  \maketitle
}

\thispagestyle{empty}
\vspace{-.1in}

\begin{abstract}
  % \lipsum[1]
\end{abstract}

\spacingset{1.5} % gives a slightly more margin between abstract and introduction

% \section{Tree of Contents}
% \input{forest.tex}
% \clearpage


\section{Introduction}

\input{Introduction/how-wto-works.tex}
\input{Introduction/composite-characteristics.tex}
\input{Introduction/strategic-citation.tex}
\input{Introduction/motiviation.tex}
\input{Introduction/diffcult-to-map.tex}
\input{Introduction/solution/proxy-and-justification.tex}
\input{Introduction/methodology/neural-network-design.tex}
\input{Introduction/conclusion/assessment.tex}


\section{Data}
\input{Data/intro.tex}

% \subsection{General Explain}
% \input{Data/general-explain.tex}

\subsection{Factual Aspect}
\input{Data/Factual Aspect/main.tex}

\subsection{Cited Articles}
\input{Data/Cited Articles/main.tex}

\section{Methodology}
\subsection{Limits of Naive Approach}

\begin{itemize}
  \item Compare co-occurrences/neural network approach.

  \item Show that co-occurrences approach isn't accurate.
\end{itemize}


\section{Empirical Findings}

\begin{itemize}
  \item No Greeks. English. Three Networks.
\end{itemize}

\input{Figures/Three-subsystems/market-access.tex}

\section{Conclusion}
This paper shows how WTO works.

\begin{itemize}
  \item Implicaiton of thie method in general.
  \item Address the imbalance of legal capacity between developed/ing countries
\end{itemize}

\clearpage

\bibliography{bibtemplate}

\clearpage
\begin{appendices}
\section{}
\label{sec:appendix}
% \subsection{Table of Contents of the Panel Report}
% \input{Data/examples/table-of-content-panel.tex}


\subsection{Factual Aspect Example}
\label{sub:factual-aspect-example}
\input{Data/examples/factual-aspect.tex}

\subsection{Collected Cited Articles for 143 WTO DSB Cases}
DS refers to \textit{Dispute Settelement} and this notation is officially adopted by WTO DSB.\\
WTO DSB identifies each dispute with a unique number for each case such as DS2 and DS18.
\label{sub:cited-articles-table}
\input{Data/examples/cited-articles-table.tex}

\subsection{Technical Details}
\label{sub:technicial-details}

\input{Figures/heatmap.tex}

% \input{coo.tex}
\end{appendices}
% == END
\end{document}